%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
%
% Packages and other includes
% Pagination
\usepackage[letterpaper, margin=1in]{geometry}
%
% Fonts
\usepackage[T1]{fontenc} % best for Western European languages
\usepackage{lmodern} % Latin Modern instead of CM
\usepackage{textcomp} % required to get special symbols
%
% Math
\usepackage{amsmath, amssymb}
\usepackage{braket}
%
% Graphics, floats, tables
\usepackage{graphicx, color, float, array}
%
% Hyperlinks
\usepackage{hyperref}
%
%
% Definitions and settings
% Paragraph indent and spacing
\setlength{\parskip}{0.4\baselineskip}
\setlength{\parindent}{0in}
%
%
% Title, authors, date
\title{\textbf{Worksheet 1}}
\date{\vspace{-2em}\today}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\begin{document}

\maketitle

%1. Review: Balancing chemical equations.
%\begin{enumerate}
%\item[a)] \,\,\, C$_6$H$_{12}$O$_6$(s) + \,\,\, O$_2$(g) $\rightarrow$ \,\,\, CO$_2$(g) + \,\,\, O$_2$(g)
%  %combustion reaction
%\item[b)] \,\,\, C$_2$H$_6$(g) + \,\,\, O$_2$(g) $\rightarrow$ \,\,\, CO$_2$(g) + \,\,\, H$_2$O
%\item[c)] \,\,\, CuS(s) + \,\,\, HNO$_3$(aq) $\rightarrow$ \,\,\, CuSO$_4$(aq) + \,\,\, NO$_2$(g)
%  %extracting copper from the mineral covellite (CuS); Oxidation-reduction reaction
%\end{enumerate}

1. Define state function. Determine whether the following are state functions:
\begin{enumerate}
\item[a)] $q + w$ % yes
\item[b)] $\Delta H$ % yes
\item[c)] $q$ % no
\item[d)] Volume % no
\end{enumerate}

2. Which statement is true of the internal energy of a system and its
surroundings during an energy exchange with a positive $\Delta E_\text{sys}$?
\begin{enumerate}
\item[a)] The internal energy of the system increases, and the internal
  energy of the surroundings decreases.
\item[b)] The internal energy of both the system and the surroundings
  increases.
\item[c)] The internal energy of both the system and the surroundings
  decreases.
\item[d)] The internal energy of the system decreases, and the internal
  energy of the surroundings increases.
\end{enumerate}
% a)

3. A system absorbs 196 kJ of heat, and the surroundings do 117 kJ
of work on the system. What is the change in internal energy of
the system?
% 313 kJ

\vspace{1in}

4. The air within a piston equipped with a cylinder absorbs 565 J of 
heat and expands from an initial volume of 0.10 L to a final volume of
 0.85 L against an external pressure of 1.0 atm. What is the change in
 internal energy of the air within the piston?
% 489 J
\end{document}
